# Read data


## Facebook ad metrics data

```{r}
df1 <-
  "C:/Users/chanb/Box Sync/Facebook pilot - Statisticians/Lifetime ad performance by ad-day 6.23.17.csv" %>% 
  read.csv(stringsAsFactors = FALSE) %>% 
  filter(Ad != "All")
oldnames <- names(df1)
newnames <- c("date",
              "ad",
              "cost",
              "reach",
              "costPerKReached",
              "impressions",
              "cpm",
              "linkClicks",
              "ctr",
              "cpc",
              "uniqueLinkClicks",
              "uniqueCTR",
              "costPerUniqueLinkClick",
              "clicksAll",
              "ctrAll",
              "cpcAll",
              "uniqueClicksAll",
              "uniqueCTRAll",
              "costPerUniqueClickAll",
              "reactions",
              "comments",
              "shares")
names(df1) <- newnames
df1 <-
  df1 %>% 
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>% 
  mutate(image = factor(gsub("\\s-.*", "", ad)),
         text = factor(gsub(".*-\\s", "", ad))) %>% 
  mutate(text = gsub("Social norms", "SocialNorms", text)) %>% 
  mutate(text = factor(text)) %>% 
  mutate(image = relevel(image, ref = "Computer"),
         text = relevel(text, ref = "Incentive"))
```

Column name mapping.

```{r}
data.frame(old = c(oldnames, NA, NA), new = names(df1)) %>% kable
```

Summarize.

```{r}
df1 %>% 
  group_by(image, text) %>% 
  summarize(nDays = n(), minDate = min(date), maxDate = max(date)) %>% 
  kable
```


## Survey data

Notes on the REDCap identifier variables:

* If `[consent] == 1`, they started the eligibility survey; 
  * if `== 0` or `== NA`, they didn't.
* If `[consent_and_eligibility_complete] == 2`, they finished the screener (whether eligible or ineligible); 
  * if `== 0`, they dropped out or never started.
* If `[eligible] == 1`, they completed the screener and were eligible; 
  * if `== 0`, they completed and were ineligible;
  * if `== NA` , they dropped out or never started.
* If `[veterans_and_social_media_use_co] == 2`, they finished the survey; 
  * if `== 0`, they dropped out or never started (this includes people who were ineligible or didn't consent).
* If `[analytic_sample] == 0`, they completed the survey but were disqualified for data quality reasons; 
  * if `== 1`, they completed survey and was not disqualified for data quality reasons;
  * if `== NA`, they didn't complete the survey.

```{r}
df2 <-
  "C:/Users/chanb/Box Sync/Facebook pilot - Statisticians/REDCap dataset.csv" %>% 
  read.csv(stringsAsFactors = FALSE)
df2 %>% 
  group_by(consent, 
           consent_and_eligibility_complete, 
           eligible, 
           veterans_and_social_media_use_co, 
           analytic_sample) %>% 
  summarize(n = n()) %>% 
  kable
```

Inclusion criteria

* Respondents who consented
* Eligible, ineligible, or missing eligibility indicator

**`r sprintf("Number included: n = %d", df2 %>% filter(consent == 1) %>% nrow)`**

Cleaning

* Parse out `fba` into 2 separate variables for `image` and `text`
* Assign indicator for survey participation, `indSurveyParticipation`
  * `analytic_sample == 1`: Participant completed survey and was not disqualified for data quality reasons
* Assign indicator for eligibility screener participation, `indScreenerParticipation`
  * `eligible == 1`: Participant completed eligibility screener and was eligible to participate in full survey
* Score the DSI-SS inventory
  * See [Joiner 2002](http://www.sciencedirect.com/science/article/pii/S0005796701000171)
  * *Scores on each item range from 0 to 3 and, for the inventory, from 0 to 12, with higher scores reflecting greater severity of suicidal ideation.*

```{r}
df2 <-
  df2 %>% 
  filter(consent == 1) %>% 
  mutate(image = 
           substr(fba, 1, 1) %>%
           factor(levels = c("c", "f", "v"),
                  labels = c("Computer", "Family", "Veteran")),
         text = 
           substr(fba, 2, 4) %>% 
           factor(levels = c("inc", "alt", "emp", "sha", "soc"),
                  labels = c("Incentive", "Altruism", "Empowerment", "Sharing", "SocialNorms"))) %>% 
  mutate(indSurveyParticipation = case_when(is.na(.$analytic_sample) ~ FALSE,
                                            .$analytic_sample == 1 ~ TRUE, 
                                            TRUE ~ FALSE)) %>%
  mutate(indScreenerParticipation = case_when(is.na(.$eligible) ~ FALSE,
                                              .$eligible == 1 ~ TRUE,
                                              TRUE ~ FALSE)) %>% 
  mutate(dsiss = dsiss_thoughts + dsiss_plans + dsiss_control + dsiss_impulses)
df2 %>% 
  group_by(image, text) %>% 
  summarize(n = n()) %>% 
  kable
df2 %>% 
  group_by(analytic_sample, indSurveyParticipation) %>% 
  summarize(n = n()) %>% 
  kable
df2 %>% 
  group_by(eligible, indScreenerParticipation) %>% 
  summarize(n = n()) %>% 
  kable
df2 %>% 
  group_by(indSurveyParticipation, indScreenerParticipation) %>% 
  summarize(n = n()) %>% 
  kable
```

### Use of VA health services

```{r}
df2 %>% 
  mutate(desc = "Before recoding") %>% 
  group_by(desc, va_ever_enrolled, va_use_12mo) %>% 
  summarize(n = n()) %>% 
  kable
```

Recoding logic

* Primary analysis will code `9` (not sure) as `0` (No)
* Sensitivity analysis will exclude the `9` values from the analysis
* If `va_ever_enrolled == FALSE` & `is.na(va_use_12mo)`, then recode `va_use_12mo` to `FALSE`
* If `va_use_12mo == TRUE` & `va_ever_enrolled == FALSE`, then recode `va_ever_enrolled` to `TRUE`

```{r}
df2 <-
  df2 %>%
  mutate(va_ever_enrolled = case_when(is.na(.$va_ever_enrolled) ~ NA,
                                      .$va_ever_enrolled == 9 ~ FALSE, 
                                      TRUE ~ as.logical(.$va_ever_enrolled))) %>%
  mutate(va_use_12mo = case_when(is.na(.$va_use_12mo) ~ NA,
                                 .$va_use_12mo == 9 ~ FALSE, 
                                 TRUE ~ as.logical(.$va_use_12mo)))
weirdRows <- which(df2$va_ever_enrolled == FALSE & is.na(df2$va_use_12mo))
df2 <- 
  df2 %>% 
  mutate(va_use_12mo = case_when(is.na(.$va_ever_enrolled) & is.na(.$va_use_12mo) ~ NA,
                                 row_number() %in% weirdRows ~ FALSE,
                                 TRUE ~ .$va_use_12mo))
weirdRows <- which(df2$va_ever_enrolled == FALSE & df2$va_use_12mo == TRUE)
df2 <- 
  df2 %>% 
  mutate(va_ever_enrolled = case_when(is.na(.$va_ever_enrolled) & is.na(.$va_use_12mo) ~ NA,
                                      row_number() %in% weirdRows ~ TRUE,
                                      TRUE ~ .$va_ever_enrolled))
df2 %>% 
  mutate(desc = "After recoding") %>% 
  group_by(desc, va_ever_enrolled, va_use_12mo) %>%
  summarize(n = n()) %>% 
  kable
```

### Presence of suicidality

DSI-SS score $\ge$ 2 (this cut-off score was chosen based on recommendations for population-based samples noted in [von Glischinski M Clin Psychol Psychotherapy 2015]

```{r}
df2 <-
  df2 %>%
  mutate(indDSISS = dsiss >= 2) 
df2 %>% 
  filter(!is.na(dsiss)) %>% 
  group_by(indDSISS, dsiss) %>% 
  summarize(n = n()) %>% 
  kable(digits = 3)
df2 %>% 
  filter(!is.na(dsiss)) %>% 
  group_by(indDSISS) %>% 
  summarize(n = n()) %>%
  mutate(freq = n / sum(n)) %>%
  kable(digits = 3)
```
